---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# teaTasteR

<!-- badges: start -->
<!-- badges: end -->

The goal of teaTasteR is to take a dataset and create a "Lady Tasting Tea" lineup plot 
for doing individual visual inference.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kmaurer/teaTasteR")
```
## Example

In the following example we will demonstrate LTT lineups for testing for independence
between carat weight and price from the ggplot2 diamonds data

```{r example}
library(teaTasteR)
## basic example code
set.seed(12345)
small_diamonds <- ggplot2::diamonds[sample(1:nrow(ggplot2::diamonds),100),]
head(small_diamonds)
```

We will feed it through the `make_lineup_dat()` function to prepare the data for plotting

```{r dataconvert}
diamonds_lineup_dat <- make_lineup_dat(M=6, dat=small_diamonds,
                                       xname="carat", yname="price")
head(diamonds_lineup_dat)
```

Then put into lineup plot. 

```{r pressure}
tt_lineup_plot(diamonds_lineup_dat)
```
